### 2021-08-13 paper/paper.tex
split one sentence into two in Section 4.1.1

As demonstrated in Section~\ref{sec:performance-comparison},
Julia is not generically slower than traditional high-performance programming
languages such as C, C++, and Fortran. A minor exception is due to
Julia being built on top of LLVM, which does not perform the same optimizations as other
C/C++/Fortran compilers. In particular, LLVM does
not use fused multiply-add (FMA) instructions by default, while GCC and Intel
compilers do, and thus one needs to opt-in to these optimizations explicitly.
Relying on Julia's code manipulation techniques, this can be achieved by using the macro
\lstinline{@muladd}\footnote{\url{https://github.com/SciML/MuladdMacro.jl}}.

>>>>

As demonstrated in Section~\ref{sec:performance-comparison},
Julia is not generically slower than traditional high-performance programming
languages like C, C++, and Fortran. A minor exception is due to
Julia being built on top of LLVM, which does not perform the same optimizations as other
C/C++/Fortran compilers. In particular, LLVM does
not use fused multiply-add (FMA) instructions by default, while GCC and Intel
compilers do. Thus, one must opt-in to these optimizations explicitly.
Relying on Julia's code manipulation techniques, this can be achieved with the macro
\lstinline{@muladd}\footnote{\url{https://github.com/SciML/MuladdMacro.jl}}.
